\emph{icepack}: a novel glacier flow modeling package

### 2019-10-09 icepack.tex
Explaining tradeoffs of variational principles

>>>>

Using variational principles to express all constitutive laws is less flexible than specifying the sliding law directly and this is a distinct disadvantage.
We were able to implement a sliding law that exhibits many of the characteristics of the Schoof sliding law.
\citet{asay2016experimental} also suggest using a sliding law that transitions sharply to exact plasticity above the critical speed.
Expressing this sliding law in UFL requires a conditional in the velocity and is thus no longer differentiable.
This lack of differentiability makes the forward solver crash.
The numerical advantages of using variational principles are so great, however, that we view this tradeoff as acceptable.
